\documentclass[conference,a4paper,english]{IEEEtran}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{tgpagella}
\usepackage[scale=0.9]{tgcursor}
\usepackage[official]{eurosym}
\usepackage{graphicx}
\graphicspath{{./img/}}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}
\usepackage{csquotes}
\usepackage{flushend} 
\usepackage{hologo}
\usepackage[backend=biber,%
  hyperref,%
  alldates=iso8601,%
  %backref,%
  %backrefstyle=none,%
  style=numeric,%
  sorting=nyt,%
]{biblatex}
\ExecuteBibliographyOptions{doi=false,url=false}
\newbibmacro{string+doiurlisbn}[1]{%
  \iffieldundef{doi}{%
    \iffieldundef{url}{%
      \iffieldundef{isbn}{%
        \iffieldundef{issn}{%
          #1%
        }{%
          \href{https://books.google.com/books?vid=ISSN\thefield{issn}}{#1}%
        }%
      }{%
        \href{https://books.google.com/books?vid=ISBN\thefield{isbn}}{#1}%
      }%
    }{%
      \href{\thefield{url}}{#1}%
    }%
  }{%
    \href{http://dx.doi.org/\thefield{doi}}{#1}%
  }%
}
\DeclareFieldFormat*{title}{\usebibmacro{string+doiurlisbn}{\mkbibquote{#1}}}

\bibliography{../bibliography.bib}
\usepackage[group-digits=integer,%
  group-minimum-digits=4,%
  list-final-separator={, and },%
  add-integer-zero=false,%
  free-standing-units,%
  unit-optional-argument,%
  binary-units,%
  detect-weight=true,%
  detect-inline-weight=math,%
]{siunitx}
%\SendSettingsToPgf
\usepackage{minted}
\setminted{%
  autogobble,%
  breaklines=true,%
  fontsize=\small,%
  linenos=false,%
  %xleftmargin=2em,%
  %xrightmargin=2em,%
}
\usepackage{paralist}
\usepackage{microtype}
\usepackage[disable]{todonotes}
\usepackage{hyperref}
\hypersetup{%
  pdftitle={A Beginner's Guide to Scientific Data Presentation using LaTeX},%
  pdfauthor={Stephan Lukasczyk},%
  pdfkeywords={siunitx, booktabs, data, presentation, latex, r, sweave,
    pstricks, pgfplots, lua}
  pdfsubject={},%
}

\newcommand\toolname[1]{\textsf{#1}}

\begin{document}

\title{A Beginner's Guide to Scientific Data Presentation using \LaTeX}

\author{\IEEEauthorblockN{Stephan Lukasczyk}
  \IEEEauthorblockA{IEEE Student Branch Passau\\
    94032 Passau, Germany\\
    \href{mailto:tex@lukasczyk.me}{tex@lukasczyk.me}}}

\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  Evaluating the work done for a seminar paper, a thesis, or even a scientific
  publication often forces students to present a large amount of data in a
  consistent and appropriate way.  Doing so, one will encounter many pitfalls
  due to the complexity of the task.  It can be a long-running and frustrating
  process to find out, which way works the best.  Although, we cannot provide
  universally valid rules, we want to give some hints and guidelines with this
  work.  Therefore, we present formal aspects, packages and tools, that are
  helpful when presenting the evaluation results and data in general.

  Our tools of choice are all from the \LaTeX{} universe; obviously, the formal
  aspects of data presentation are valid for other tools as well.  We show a
  variety of \LaTeX{} packages and give an introduction into their usage, in
  order to show how easy the presentation of data can be.

  Only a small knowledge of \LaTeX{} is needed to understand the source
  examples, as we try to provide all examples in a very simple and
  self-explaining way.
\end{abstract}
\begin{IEEEkeywords}
  siunitx, booktabs, data, presentation, latex, r, sweave, pstricks, pgfplots,
  lua
\end{IEEEkeywords}

\input{chapters/introduction}

\input{chapters/numbers}

\input{chapters/tables}

\input{chapters/plot-creation}

\input{chapters/plots}

\input{chapters/summary}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\printbibliography

% that's all folks
\end{document}


